\documentclass[11pt]{article}

\usepackage{xcolor}
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

\begin{document}

\textbf{\color{red}Artículos publicados}

\begin{enumerate}
\item Hevia-Orozco, J.C., Reyes-Aguilar, A., Hernández-Pérez, R., González-Santos, L., Pasay, E H., Barrios, F.A., Personality Traits Induce Different Brain 
Patterns When Processing Social and Valence Information, Frontiers in Physiology, enero de 2022, 1-9.

\item Romero-Meléndez, C. , Castillo-Fernández, D. and González-Santos, L., “On the Boundedness of the Numerical Solutions’ Mean Value in a Stochastic 
Lotka–Volterra Model and the Turnpike Property“, Hindaw Complexity, noviembre de 2021, 1-14.

\item Romero-Meléndez, C., González-Santos, L., Castillo-Fernández, “A NUMERICAL APPROACH FOR THE STOCHASTIC CONTROL OF A TWO-LEVEL QUANTUM SYSTEM”, 
CYBERNETICS 
AND PHYSICS, agosto de 2020; 9(2), 107-116.

\item Velásquez-Upegui, E.P., Tovar-González, J., González, L., “Hacia una caracterización prosódica de los actos del habla directivos: producción y 
percepción de 
mandatos”, Lengua y Habla, Revista del Centro de Investigación y Atención Lingüística C.I.A.L, agosto de 2020; 24, 1-5.

\item Muley, V.Y., Loópez-Victorio, C.J., Ayala-Sumuano, J.T., González-Gallardo, A., GonzaálezSantos, L., Lozano-Flores, C., Wray, G., Hernández-Rosales, 
M., 
Varela-Echavarría, A., “Conserved and divergent expression dynamics during early patterning of the T telencephalon in mouse and chick embryos”, Progress In 
Neurobiology, enero de 2020; 186, 1-15.

\item Martínez-Soto, J., De la Fuente Suárez, L.A., González-Santos, L., Barrios, F.A., “Observation of environments with different restorative potential 
results 
in differences in eye patron movements and pupillary size”, IBRO Reports, noviembre de 2019; 7, 52-58.

\item Nanni, M., Martínez-Soto, J., González-Santos, L., Barrios, F.A., "Neural correlates of the natural observation of an emotionally loaded video", Plos 
One, 
noviembre de 2018, 1-19.

\item Martinez J, Gonzalez-Santos L, Barrios F.A., AFFECTIVE AND RESTORATIVE VALENCES FOR THREE ENVIRONMENTAL CATEGORIES, Perceptual And Motor Skills, 
octubre de 
2014, 1-10.

\item Beatriz Moreno M., Concha L., González-Santos L., Ortiz J.J., Barrios F.A., , Correlation between Corpus Callosum Sub-Segmental Area and Cognitive 
Processes 
in School-Age Children, Plos One, agosto de 2014; 9(8), 1-10.

\item Bauer C.C., Moreno B., Gonzalez-Santos L., Concha L., Barquera S., Barrios F.A., Child overweight and obesity are associated with reduced executive 
cognitive performance and brain alterations: a magnetic resonance imaging study in Mexican children, Pediatric Obesity, julio de 2014.

\item Martínez-Soto J., González-Santos L., Pasaye E. and Barrios F.A., Exploration of neural Correlates of restorative environment exposure through 
functional 
magnetic resonance, Intelligent Buildings International, Taylor Francis Online, septiembre de 2013; 5(S1), 10-28.

\item Gonzalez-Santos L, Mercadillo RE, Graff A, Barrios FA, "Versión computarizada para la aplicación del Listado de Síntomas 90 (SCL 90) y del Inventario 
de 
Temperamento y Carácter (ITC)", Salud Mental, julio de 2007; 30(4), 31-40.

\item Barríos F.A., González L., Fávila R., Alonso M.E., Salgado P., Díaz R., Fenández, J., OLFACTION AND NEURODEGENERATION IN HD, Neuroreport, enero de 
2007; 
18(1), 73-76.

\item Huerta-Ocampo I., Mena F., Barríos F.A., Martínez G., González L., Larriva-Sahd J.L., Perinatal Exposure to Androgen Suppresses Sexual Dimorphism in 
Nerve 
Trunk Diameter, Axon Number, and Fiber Size Spectrum: a Quantitative Ultrastructural Study of the Adult Rat Mammary Nerve., Brain Research, octubre de 2005; 
1060(1-2), 179-183.

\item George-Téllez R, Segura-Valdez ML, González-Santos L, Jiménez-García LF, "Cellular organization of pre-mRNA splicing factors in several tissues. 
Changes in 
the uterus by hormone action", Biology of the cell, mayo de 2002; 94(2), 99-108.

\item González-Santos, L., Rojas-Jasso, R., Salgado, P., Ponte-Romero, R., Sánchez-Cortázar, J., Barrios, F.A., "Segmentación semiautomática de imágenes por 
resonancia magnética cerebral por crecimiento de regiones con estimación robusta: una validación radiológica", Revista Mexicana De Radiologia, abril de 
1999; 53(2), 51-54.

\end{enumerate}

\end{document}
