\textbf{Agradecimientos en Congresos Internacionales}

\hfill

\begin{enumerate}

\item Ocampo-Ruiz, A.L., Vazquez-Carrillo, D.,I., Dena-Beltrán, J., L., Cárdenas, A.G., Arellano, R., Cisneros-Mejorado, A., 
Dimas-Rufino, MA., Castillo, X., Garay, Martínez de la Escalera, E., G., Clapp, C., and Macotela, Y., “PROLACTIN RECEPTOR 
DEFICIENCY PROMOTES HYPOMYELINATION DURING CENTRAL NERVOUS SYSTEM MATURATION OF SUCKLING AND PREPUBERTAL MICE”, Seventh 
Biennial Meeting of the North American Society for Comparative Endocrinology, MAY.28-June.1, 2023.

\item Gracia-Tabuenca, Z., Días-Patiño, J.C., Arelio, I., Alcauter, S., “Topological abnormal load in ADHD functional brain 
network”, Chicago, IL, NEUROSCIENCE, 19-23, octubre de 2019.

\item Valles-Capetillo, E. and Giordano, M., “Comprehension of language in social contexts”, The Eleventh Annual Meeting of 
the Society for the Neurobiology of Language, Helsinki Finlandia, 20-22, agosto de 
2019.

\item Navarrete, E., Valles-Capetillo, E., Giordano, M., “Metaphors comprehension throughout development and its neural 
correlate”, Chicago, IL, NEUROSCIENCE, 19-23, octubre de 2019.

\item Martínez, A., Y., Demertzi, A., Bauer, C.C.C., Gracia, Z., Alcauter, S., Barrios, F.A., “Body awareness results in 
characteristics dynamic functional connectivity states”, 25th Annual Meeting of the Organization for Human Brain Mapping, 
ROMA, 9-13, junio de 2019.

\item Gracia-Tabuenca, Z., Moreno B., Barrios, F., Alcauter, S., “Functional Segregation of the Sensorymotor and Associative 
Networks in Adolescence”, 25th Annual Meeting of the Organization for Human Brain Mapping, ROMA, 9-13, junio de 2019.

\item Gracia-Tabuenca, Z., Moreno, M.B., Barrios, F.A., Alcauter, S., "Inverse relationship homotopic and intra-hemispheric 
asymmetry of intrinsic brain functional connectivity in school-age children, Society for Neuroscience, San Diego, CA, 
November 3-7, noviembre de 2018.

\item Gracia-Tabuenca, Z., Moreno, M.B., Barrios, F.A., Alcauter, S., "Hemispheric Asymmetries in FunctionalConnectivity in 
Children correlatewith Visual Attention", OHBM, Annual Meeting, Singapore, June 17-21, Créditos en: Congreso internacional, 
junio de 2018.

\item Martínez, A.Y., Bauer, C.C.C., Gracia, Z., Alcauter, S., Barrios, F.A., "From Attention to Perception: A Dynamic 
Functional Connectivity Study in Experienced Meditators", OHBM, Annual Meeting, Singapure, June 17-21, 2018.

\item Garcia-Hernandez, A., Ladron de Guevara Cervantes, D., Vasquez-Hernandez, A., AnguloPerkins, A., Nava-Gomez, L., 
Alcauter, S., “Cerebellar gray matter volume is differentiallyaffected by age in heavy marijuana users”, 23 Annual Meeting 
of the OHBM, Vancouver,Canada, junio de 2017.

\item Barrios, AF., Rodríguez, Ll., Alcauter, S, "Functional connectivity of the human claustrum",Society for Neuroscience, 
Washington, DC, EUA, noviembre de 2017.

\item Martínez, A., Bauer, C., Gracia, Z., Alcauter, S., Barrios, F. “Dynamical Functional ConnectivityStates may Detect 
Changes in Brain Patterns of Proprioception”, 23 Annual Meeting of theOHBM, Vancouver, British Columbia, Canada, junio de 2017.

\item Navarrete, E., Gracia, Z., Moreno, B., García, L., Ortiz, J.J., Barrios, F., Alcauter, S., "Executive functions 
performance correlates with fron to-parietal functional connectivity in children", 22 Annual Meeting of the OHBM, Geneva, 
Switzerland, junio de 2016.

\item Reyes-Aguilar, A., Morales-Ramirez, E., Fernandez-Ruiz, J., Barrios, F., "Thinking About Mental States of Cooperators 
and Non-Cooperators Resulting from Personal Interactions", 22nd Annual Meeting of the OHBM, Geneva, Switzerland, junio de 2016.

\item Gracia, Z., Navarrete, E., Moreno, B., Barrios, F., Alcauter S., "Local efficiency of brain's functional connectivity 
reflects longitudinal changes in temporal cortex lateralization in school-age children and adolescents", Neuroscience, San 
Diego, EUA., noviembre de 2016.

\item Navarrete, E., Gracia, Z., Barrios, F., Alcauter, S., "Functional connectivity changes throughout childhood to 
adolescence", Neuroscience, San Diego, EUA., noviembre de 2016.

\item Gracia, Z., Moreno, B., Navarrete, E., Barrios, F., Alcauter, S., "Development of Functional Connectivity Asymmetries: 
Longitudinal effects in Children and Adolescents", 22nd Annual Meeting of the OHBM. Geneva, Switzerland, junio de 2016.

\item Bauer C., Díaz, J.L., Pasaye E., Barrios F.A., “Conscious perception as the inner construct of a priori structures: 
neurophenomenology through fMRI”, OHBM Annual Meeting, Hamburg, Germany, Jun 8-12, 2014.

\item Vázquez P., Whitfield-Gabrieli S., Barrios F.A., “Elucidating dissociation in brain functional connectivity during 
hypnotic state. A rs-fMRI study”, OHBM Annual Meeting, Hamburg, Germany, Jun 8-12, 2014.

\item Pasaye E., León-Vázquez M., Rodríguez-Chávez E., Molina-Carrión E., Barrios F.A. “Resting state cortico-cerebellar networks are absent in MS 
Patients and pseudobulbar affect”, OHBM Annual Meeting, 
Hamburg, Germany, Jun 8-12, 2014.

\item León-Vázquez, M., Molina-Carrion, E., Barrios F., Pasaye, E., "Pseudobulbar Affect is an Affective Dysmetria in 
multiple Sclerosis Patients, A Connectivity Study", junio de 2013.

\item Bauer, C., Díaz, J., Concha L., Barrios, F., "Qualia in the Brain: an fMRI Approach to Neurophenomenology", junio de 2013.

\item Cavazos-Rodríguez R., Moreno B., Alcauter S., Concha L., Barrios F.A., “Hemispheric asymmetries of the Default Mode 
Network in Children”, 3 rd. Bienal Conference on Resting State Brain Connectivity, Magdeburg-Germany, September 5-7., septiembre de 2012.

\item Pasaye, E.H., Alcauter, S., Mercadillo, R.E., Bauer, C.C.C., Paz, J., Taboada, J. and Barrios, F.A., "Mirror System 
Involved in Tactile Stimuli", 18th Annual Meeting OHBM, Beijing-China, June 10-14, 2012.

\item Bauer, C.C.C, Díaz, J.L., Concha, L., Barrios, F.A, "My is the Brain: Distinct Cortical Structures for offline or 
online body representations", 18th Annual Meeting OHBM, Beijing-China, June 10-14, 2012.

\item Alcauter, S, Pasaye, E., Barrios, F.A., "Brain's white matter alterations in lower limb amputees: a DTI study", 18th 
Annual Meeting OHBM, Beijing-China, June 10-14., 2012.

\item Rodríguez-Nieto G., Mercadillo R.E., Martínez-Soto J., Barrios F.A., “Gender differences of hemodynamic responses in 
brain regions activated while experiencing compassion”, Society for Neuroscience, New Orleans-USA, October 13-17, 2012.

\item Bauer, C.C.C., Díaz, J., Pasaye, E.H., Vázquez, P.G., Concha, L., Barrios, F.A., "Sustained Attention in Absence of 
External Stimuli Evokes Somesthetic Activity in the Primary Somatosensory Cortex: A Functional MRI Study", 17th Annual 
Meeting HBM, Quebec-Canada, June 26-30, 2011.

\item Mercadillo, R.E., Diaz, J.L., Alcauter, S., Barrios, F.A., "Police culture inhibit the empathy related brain activity 
in women: A neuro-ethnographical proposal", 17th Annual Meeting of the Organization on Human Brain Mapping, Quebec-Canada, 
June 26-30, 2011.

\item Angulo-Perkins, A., Aubé, W., Peretz, I., Barrios, F, Armony, J., Concha, L., "Music-specific responses within the 
temporal lobe", 17th Annual Meeting of the Organization on Human Brain Mapping, Québec-Canada, June 26-30, 2011.

\item Torres, C.A., Pasaye, E.H., Concha, L., Barrios, F.A., "Neural correlates of attitudinal evaluation: A fMRI study of 
attitudes towards animals", 17th Annual Meeting HBM, Quebec-Canada, June 26-30, 2011.

\item Pasaye, E.H., Alcauter, S., Mercadillo, R.E., Bauer, C.C.C., Ortiz, J.J., Barrios, F.A., "Neural Correlates of Spatial 
Encoding of Sensory Stimuli in Healthy Subjects, an fMRI Study", 17th Annual Meeting HBM, Quebec-Canada, June 26-30., 
2011.

\item Romero-Romo, J. I., Romero-Cano, D., Graff-Guerrero, A., “Memantine: uncompetitive NMDA receptor ntagonist offers 
relief in patients with neuropathic pain”, International Association for the Study of Pain (IASP), 11th World Congress on 
Pain, August 21-26, Sydney, Australia, 2005.

\item Ollervides, M. A., Ortiz, J. J., Favila, G. R., Barrios, F. A., “Brain mapping of motor and imaginary motor activity 
with functional mri at 1.0 T”, SACNAS, Nacional Conference, Austin, Texas, EUA, 2004.

\item Prado-Alcalá, R., Ruiloba, M. I., Rubio, L., Solana-Figueroa, R., Galindo, L. E., Quitarte, G. L., “Interference with 
memory consolidation produced by serotonin infusions into different regions of the striatum”, Society for Neuroscience, Orlando, Florida, EUA, 
2002.

\item Romero-Romo, J., Favila, R., Salgado., P., Barrios, F.A., Brushing stimuli in lower limb amputees evoke phantom limb 
perception; a fMRI study, 2000.

\end{enumerate}

