\textbf{Agradecimientos en artículos internacionales}

\hfill

\begin{enumerate}

\item García-Vilchis, B, Román-López, T., , Ramírez-González, D., López-Camaño, X.J., Medina-Rivera, A., Alcauter, S. and 
Ruiz-Contreras, A., “TwinsMX: Exploring the Genetic and Environmental Influences on Health Traits in the Mexican 
Population”, Twin Research and Human Genetics, 27, 85–96, Créditos en: Artículo internacional, noviembre de 2024.

\item Rasgado-Toledo, J., Siddharth Duvvadab, S., Shahc, A., Ingalhalikarc, M., Allurib, GarzaVillarreal, E., “Structural 
and 
functional pathology in cocaine use disorder with polysubstance use: A multimodal fusion approach structural-functional 
pathology in cocaine use disorder”, Progress in Neuropsychopharmacology \& Biological Psychiatry, 1-7, Créditos en: 
Artículo 
internacional, noviembre de 2024.

\item Angeles-Valdez, D., Rasgado-toledo, J., Villicaña, V., Davalos Guzman, A., Almanza, C., FajardoValdez, A., 
Alcala-Lozano, R. \& Garza-Villarreal, E., “The Mexican dataset of a repetitive transcranial magnetic stimulation clinical 
trial on cocaine use disorder patients: SUDMEX tMS”, Scientific Data, Créditos en: Artículo internacional, noviembre de 
2024.

\item Luna-Munguia, H., Gasca-Martinez, Garay-Cortes, Coutiño, D., Regalado, M. De los Rios, E., VillaseñorP., 
Hidalgo-Flores, 
Flores-Guapo, K., Brandon-Yair, B., Concha, L., “Selective Medial Septum Lesions in Healthy Rats Induce Longitudinal 
Changes in Microstructure of Limbic Regions, Behavioral Alterations, and Increased Susceptibility to Status Epilepticus”, 
Molecular Neurobiology (2024) 61:7898–7918, Créditos en: Artículo internacional, noviembre de 2024.

\item Vázquez, P. G. , Whitfield-Gabrieli, S., Bauer, C.C. and Barriosa, F. A., “Brain functional connectivity of hypnosis 
without target suggestion. An intrinsic hypnosis rs-fMRI study”, THE WORLD JOURNAL OF BIOLOGICAL PSYCHIATRY, VOL. 25, NO. 
2, 95–105, Créditos en: Artículo internacional, noviembre de 2024.

\item Rodríguez-Vidal, LL., Alcauter, S., Barrios, F.A., “The functional connectivity of the human claustrum, according to 
the 
Human Connectome Project database”, PLOS ONE, Créditos en: Artículo internacional, abril de 2024.

\item Reyes-Pérez, P., Hernández-Ledesma, A.L., Román-López, T.V., García-Vilchis, B., Alcauter, S., “Building national 
patient registries in Mexico: insights from the MexOMICS Consortium”, frontiers, 1-14, Créditos en: Artículo internacional, junio de 2024.

\item Trujillo-Villarreal, Cruz-Carrillo, G., Angeles-Valdez, D., Garza-Villarreal, E.A., Camacho-Morales, A., “Paternal 
Prenatal and Lactation Exposure to a High-Calorie Diet Shapes Transgenerational Brain Macro- and Microstructure Defects, 
Impacting Anxiety-Like Behavior in Male Offspring Rats”, eNeuro, 1-22, Créditos en: Artículo internacional, febrero de 
2024.

\item Garcia-Saldivar, P. , De León, C., Mendez Salcido, F.A., Concha, L., Hugo Merchant, H., “White matter structural 
bases 
for phase accuracy during tapping synchronization”, eLife, 1-27, Créditos en: Artículo internacional, noviembre de 2024.

\item Fajardo-Valdez, A., Camacho-Téllez. V., Rodríguez-Cruces, García-Gomar, Pasaye, E.H., Concha, L., Functional 
correlates 
of cognitive performance and working memory in temporal lobe epilepsy: Insights from task-based and resting-state fMRI”, 
PLOS ONE, 1-20, Créditos en: Artículo internacional, marzo de 2024.

\item Olalde-Mathieu, V.E., Licea-Haquet, G.,L., Alcauter, S., Atilano-Barbosa, D., Dominquez-Frausto, C., A., 
Angulo-Perkins, A., Barrios, F.A., “Empathy-related differences in the anterior cingulate functional connectivity of 
regular cannabis users when compared to controls”, Neuroscience Research, 1-9, 2023, Créditos en: Artículo internacional, 
diciembre de 2023.

\item Rasgado-Toledo, J., Siddharth-Duvvadab, S., Shahc, A. , Ingalhalikarc, M. , Allurib, V., GarzaVillarreal, E.A., 
“Structural and functional pathology in cocaine use disorder with polysubstance use: A multimodal fusion approach 
structural-functional pathology in cocaine use disorder”, Progress in Neuropsychopharmacology \& Biological Psychiatry, 
1-8, 
2023, Créditos en: Artículo internacional, noviembre de 2023.

\item Cruz-Carrillo, G., Trujillo-Villarreal, L.A., Angeles-Valdez, D., Concha, L.,Eduardo Garza-Villarreal, E.A., 
Camacho-Morales, A., “Prenatal Cafeteria Diet Primes Anxiety-like Behavior Associated to Defects in Volume and Difusion in 
the Fimbria-fornix of Mice Ospring”, NEUROSCIENCE, 70-85, 2023, Créditos en: Artículo internacional, noviembre de 2023.

\item Román-López, T. V., García-Vilchis, B. , Murillo-Lechuga, V. , Chiu-Han, E., López-Camaño, X. , Aldana-Assad, O. , 
Diaz-Torres, S., 5 , Caballero-Sánchez, U., Ivett Ortega-Mora, Ramírez-González, D., Zenteno, D. , Espinosa-Valdés, Z., 
Tapia-Atilano, A. , Pradel-Jiménez, S., Rentería, M.E., MedinaRivera, A., Ruiz-Contreras, A.E., Alcauter, S., “Estimating 
the Genetic Contribution to Astigmatism and Myopia in the Mexican Population”, CAMBRIDGE, University Press, 1-9, 2023, 
Créditos en: Artículo internacional, noviembre de 2023.

\item Villaseñor, P. J., Cortés-Servín, D., Pérez-Moriel, A., Aquiles, A., Luna-Munguía, H., RamirezManzanares, A., 
Coronado-Leija, R., Larriva-Sahd, J., 1 and Concha, L., “Multi-tensor diffusion abnormalities of gray matter in an animal 
model of cortical dysplasia”, frontiers, 1-10, 2023, Créditos en: Artículo internacional, noviembre de 2023.

\item Vázquez, P.G., Whitfield-Gabrieli, S., Bauer, C.C.C. \& Barrios, F.A., “Brain functional connectivity of hypnosis 
without target suggestion. An intrinsic hypnosis rs-fMRI study”, The World Journal of Biological Psychiatry, 1-12, 2023, 
Créditos en: Artículo internacional, noviembre de 2023.

\item Gracia-Tabuenca, Z., Díaz-Patiño, J.C., Arelio-Ríos,I., Moreno-García, M.B., Barrios, F.A. and Alcauter, S., 
“Development of the Functional Connectome Topology in Adolescence: Evidence from Topological Data Analysis”, eNeuro, 1-10, 
2023, Créditos en: Artículo internacional, noviembre de 2023.

\item Atilano-Barbosa, D. and Barrios, F.A., “Brain morphological variability between Whites and African Americans: the 
importance of racial identity in brain imaging research”, frontiers, 1-15, 2023, Créditos en: Artículo internacional, 
diciembre de 2023.

\item Llamas-Alonso, L.A., Barrios, F.A., González-Garrido A., Ramos-Loyo J., “ Emotional faces interfere with saccadic 
inhibition and attention re-orientation: An fMRI study”, Neuropsychologia, 1-9, Créditos en: Artículo internacional, 
diciembre de 2022.

\item Rodríguez-Nieto, G., Mercadillo, R.E., Pasaye, E.H., and Fernando A. Barrios, F.A., “Affective and cognitive 
brain-networks are differently integrated in women and men while experiencing compassion”, Frontiers in Psychology, 1-12, 
Créditos en: Artículo internacional, diciembre de 2022.

\item Olalde-Mathieu, V.E., Sassi, F., Reyes-Aguilar, A., Mercadillo, R.E., Alcauter, S., Barrios., A.F., 
“Greater Empathic Abilities and Resting State Brain Connectivity Differences in Psychotherapists Compared to 
Non-psychotherapists”, Neuroscience, 1-10, Créditos en: Artículo internacional, diciembre de 2022.

\item Olalde-Mathieu, V.E., Licea-Haquet, G., Reyes-Aguilar, A. \& Barrios, F.A., “Psychometric properties of the Emotion 
Regulation Questionnaire in a Mexican sample and their correlation with empathy and alexithymia”, Cogent Psychology, 1-11, 
Créditos en: Artículo internacional, diciembre de 2022.

\item Aguilar-Moreno, A., Ortiz, J., Concha, L., Alcauter, S., Paredes, R.G., “Brain circuits activated by female sexual 
behavior evaluated by manganese enhanced magnetic resonance imaging”, PLOS ONE, 1-24, Créditos en: Artículo internacional, 
agosto de 2022.

\item Domínguez-Arriola, M. E., Olalde-Mathieu, V. E., Garza-Villarreal, E.A., Barrios, F.A, “The Dorsolateral Prefrontal 
Cortex Presents Structural Variations Associated with Empathy and Emotion Regulation in Psychotherapists”, Brain 
Topography, 1-14, 21, Créditos en: Artículo internacional, agosto de 2022.

\item Hevia-Orozco, J., Azalea Reyes-Aguilar, A., Pasaye, E.H., Barrios, F.A, “Participation of visual association areas in 
social processing emerges when rTPJ is inhibited”, eNeurologicalSci 27, 1-6, Créditos en: Artículo internacional, diciembre 
de 2022.

\item Lizcano-Cortés, F., Rasgado-Toledo, J., Giudicessi, A. and Giordano, M., “Theory of Mind and Its Elusive Structural 
Substrate”, frontiers in Human Neuroscience, p1-9, Vol. 15, Créditos en: Artículo internacional, noviembre de 2021.

\item Rasgado-Toledo, J., Lizcano-Cortés, F., Víctor Olalde-Mathieu, V.E., Licea-Haquet, G., Zamora-Ursulo, M.A., Giordano, 
M. and Reyes-Aguilar, A., “A Dataset to Study Pragmatic Language and Its Underlying Cognitive Processes”, frontiers in 
Human Neuroscience, p1-7, Vol. 15, Créditos en: Artículo internacional, noviembre de 2021.

\item Martínez, A.Y., Demertzi, A., Bauer, C.C.C., Gracia-Tabuenca, Z., Alcauter, S., and Barrios, F.A., “The Time Varying 
Networks of the Interoceptive Attention and Rest”, eNeuro, p1-13, Créditos en: Artículo internacional, noviembre de 2021.

\item Domínguez-Arriola, M.E., Víctor E. Olalde-Mathieu, V.E., Garza-Villareal, E.A., Barrios, F.A., “The Dorsolateral 
Prefrontal Cortex Presents Structural Variations Associated with Empathic Capacity in Psychotherapists“, bioRxiv, p1-19, 
Créditos en: Artículo internacional, noviembre de 2021.

\item Lazcano, I., Cisneros-Mejorado, A., Concha, L., José Ortiz-Retana, J.J., Garza-Villarreal, E.A. \& Orozco, A., “MRI- 
and histologically derived neuroanatomical atlas of the Ambystoma mexicanum (axolotl)”, Scientific Reports, p1-13, Créditos 
en: Artículo internacional, noviembre de 2021.

\item Luna-Munguia, H., Marquez-Bravo, L., Concha, L., “Longitudinal changes in gray and white matter microstructure during 
epileptogenesis in pilocarpine-induced epileptic rats”, Seizure: European Journal of Epilepsy, 90, p130-140., Créditos en: 
Artículo internacional, noviembre de 2021.

\item Garcia-Saldivar, P., Garimella, A., Garza-Villarreal, E.A., Mendez, F.A., Concha, L., Merchant, H., “PREEMACS: 
Pipeline 
for preprocessing and extraction of the macaque brain surface”, NeuroImage, 227, p1-16., Créditos en: Artículo 
internacional, noviembre de 2021.

\item López-Gutiérrez, M.F., Gracia-Tabuenca, Z., Ortiz, J.J., Camacho, F.J., Young, L.J., Paredes, R.G., Díaz, N.F., 
Portillo, W., Alcauter, S., “Brain functional networks associated with social bonding in monogamous voles”, eLife, p1-25, 
Créditos en: Artículo internacional, noviembre de 2021.

\item Gracia-Tabuenca, Z., Moreno, M.B., Barrios, F.A., Alcauter, S., “Development of the brain functional connectome 
follows 
puberty-dependent nonlinear trajectories”, NeuroImage, 229, p1-9, Créditos en: Artículo internacional, noviembre de 2021.

\item Rodríguez-Cruces, R., Bernhardt, B. C., Concha, L., “Multidimensional associations between cognition and connectome 
organization in temporal lobe epilepsy”, NeuroImage (213)1-11, Créditos en: Artículo internacional, marzo de 2020.

\item Niño, S. A., Erika Chi-Ahumada, E., Ortíz, J., Zarazua, S., Concha, L., Jiménez-Capdeville, M.E., “Demyelination associated with chronic arsenic exposure in Wistar rats”, Toxicology and Applied 
Pharmacology, (393)1-9, 2020., Créditos en: Artículo internacional, marzo de 2020.

\item García-Gomar, M.G., Concha, L., Soto-Abraham, J., Tournier, J. D., Aguado-Carrillo, G., VelascoCampos, F., “Long-Term 
Improvement of Parkinson Disease Motor Symptoms Derived From Lesions of Prelemniscal Fiber Tract Components”, OPERATIVE 
NEUROSURGERY, Vol. 0, Num. 0, 1-12, Créditos en: Artículo internacional, abril de 2020.

\item Gracia-Tabuenca, Z., Juan Carlos Díaz-Patiño, J.C., Arelio, I.,2 and Alcauter, S., “Topological Data Analysis Reveals 
Robust Alterations in the Whole-Brain and Frontal Lobe Functional Connectomes in Attention-Deficit/Hyperactivity Disorder”, 
March-April, 7(2) ENEURO, 1–10, Créditos en: Artículo internacional, marzo de 2020.

\item Hatton, S. N., Huynh, K. H., Bonilha, L., Abela, E., Alhusaini, S., Altmann, A., Alvim, M. K. M., Akshara R. 
Balachandra, A. R., Concha, L., “White matter abnormalities across different epilepsy syndromes in adults: an 
ENIGMA-Epilepsy study”, BRAIN, A Journal of Neurology, 1-20, Créditos en: Artículo internacional, abril de 2020.

\item Rojas-Vite, G., Coronado-Leija, R., Narvaez-Delgado, O., Ramírez-Manzanares, A., Marroquín, J.L., Noguez-Imm, R., 
Aranda, M.L, Sherrer, B., Larriva-Sahd, J., Concha, L., “Histological validation of per-bundle water diffusion metrics 
within a region of fiber crossing following axonal degeneration”, NeuroImage, 201, Créditos en: Artículo internacional, 
noviembre de 2019.

\item Angulo-Perkins, A., Concha, L., “Discerning the functional networks behind processing of music and speech through 
human 
vocalizations”, PLOS-ONE, Créditos en: Artículo internacional, octubre de 2019.

\item Narvaez-Delgado, O., Rojas-Vite, G., Coronado-Leija, R., Ramírez-Manzanares, A., Marroquín, J.L., Noguez-Imm, R., 
Aranda, M.L, Sherrer, B., Larriva-Sahd, J., Concha, L., “Histological and diffusion-weighted magnetic resonance imaging 
data from normal and degenerated optic nerve and chiasm of the rat”, Data in brief, 26, 1-19, Créditos en: Artículo 
internacional, noviembre de 2019.

\item Manno, F.A.M, Raul R. Cruces,R.R., Lau, C. and Barrios, F.A., “Uncertain Emotion Discrimination Differences Between 
Musicians and Non-musicians Is Determined by Fine Structure Association: Hilbert Transform Psychophysics”, frontiers in 
Neuroscience,1-13, Créditos en: Artículo internacional, noviembre de 2019.

\item Rodríguez-Cruces, R., Bernhardt, B.C., Luis Concha, L., “MULTIDIMENSIONAL ASSOCIATIONS BETWEEN COGNITION AND 
CONNECTOME 
ORGANIZATION IN TEMPORAL LOBE EPILEPSY”, COGNITIVE CONNECTOMICS IN TLE, bioRxiv, June, 1-25, Créditos en: Artículo 
internacional, noviembre de 2019.

\item CCC, Bauer, Whitfield-Gabrieli S, Díaz JL, Pasaye EH, Barrios FA, “From state-to-trait meditation: Reconfiguration of 
central executive and default mode networks”, eNeuro, 1-20, Créditos en: Artículo internacional, noviembre de 2019.

\item Hernández-Abrego, A., Vázquez-Gómez, E., García-Colunga, J., "Effects of the antidepressant mirtazapine and zinc on 
nicotinic acetylcholinereceptors", Neuroscience Letters 665, 1-6, 2018. , Créditos en: Artículo internacional, noviembre de 
2018.

\item Mercadillo, R.E., Alcauterc, S., Barrios, F.A., "Effects of primatological training on anthropomorphic valuations of 
emotions", IBRO Reports 5, 54–59, 2018., Créditos en: Artículo internacional, noviembre de 2018.

\item Ortiz, J.J., Portillo, W., Paredes, R.G., Young, L.J, Alcauter, S., "Resting state brain networks in theprairie 
vole", 
SCiENTifiC REPOrTS, 8:1-11, 2018., Créditos en: Artículo internacional, noviembre de 2018.

\item Gracia-Tabuenca, Z., Moreno, M.B., Barrios, F.A., Alcauter, S., "Hemispheric asymmetry and homotopy of resting state 
functionalconnectivity correlate with visuospatial abilities in school-age children", NeuroImage 174, 441–448, 2018. , 
Créditos en: Artículo internacional, noviembre de 2018.

\item Rodríguez-Cruces, R, Velázquez-Pérez, L., Rodríguez-Leyva, I., Velasco, A.L.,Trejo-Martínez, D., Barragán-Campos, 
H.M., 
Camacho-Téllez, V., Concha, L., "Association of white matter diffusion characteristics and cognitivedeficits in temporal 
lobe epilepsy", Epilepsy \& Behavior 79, 138–145, 2018., Créditos en: Artículo internacional, noviembre de 2018.

\item Sarael Alcauter, Liliana García-Mondragóna, Zeus Gracia-Tabuenca, Martha B. Moreno, Juan J.Ortiza, Fernando A. 
Barrios, 
“Resting state functional connectivity of the anterior striatum andprefrontal cortex predicts reading performance in 
school-age children”, Brain and Language, 174(94-102), Créditos en: Artículo internacional, junio de 2017.

\item Reyes-Aguilar, A., Fernández-Ruiz, J., Pasaye, E.H., Barrios, F. A., “Executive Mechanisms forThinking about Negative 
Situations in both cooperative and non-cooperative contexts”, Frontiersin Human Neuroscience, 11(1-5), Créditos en: 
Artículo internacional, mayo de 2017.

\item Angulo-Perkins A., William Aubé W., Peretz I., Barrios F.A. , Armony J.L. and Concha L., “Music listening engages 
specific cortical regions within the temporal lobes: Differences between musicians and non-musicians”, CORTEX, 59, 
126-137., Créditos en: Artículo internacional, septiembre de 2014.

\item Bauer C.C.C., Díaz J.L, Concha L., Barrios F.A., “Sustained attention to spontaneous thumb sensations activates brain 
somatosensory and other proprioceptive areas”, Brain and Cognition 87, 86–96., Créditos en: Artículo internacional, 
septiembre de 2014.

\item Martínez-Soto J., Montero M.E., Córdova A., “Restauración psicológica y naturaleza urbana: algunas implicaciones para 
la salud mental”, Salud Mental, 37, 217-224, Créditos en: Artículo internacional, mayo de 2014.

\item Donnet S., Bartolo R., Fernández J.M., Silva Cunha J.P., Prado L., and Merchant H., “Monkeys time their pauses of 
movement and not their movement-kinematics during a synchronizationcontinuation rhythmic task", J Neurophysiol 111: 
2138–2149., Créditos en: Artículo internacional, septiembre de 2014.

\item Sánchez-Resendis O., Medina A.C., Serafín N., Prado-Alcalá R.A., Roozendaal B., Quirarte G.L., 
“Glucocorticoid-cholinergic interactions in the dorsal striatum in memory consolidation of inhibitory avoidance traning”, 
frontiers in Behavioral Neuroscience, Vol. 6, 1-6., Créditos en: Artículo internacional, noviembre de 2012.

\item Mercadillo R.E., Trujillo C., Sánchez-Cortazar J., Barrios F.A., “Brain activity in adhd patients performing the 
counting stroop task: A social neuroscience approach”, Phychological Reports: Disability and Trauma, 111,2,652-668., 
Créditos en: Artículo internacional, septiembre de 2012.

\item Alcauter, S, Barrios, F. A., Díaz, R, Fernández-Ruiz, J., "Gray and white matter alterations in spinocerebellar 
ataxia 
type 7: An in vivo DTI andVBM study", NeuroImage 55 1–7, Créditos en: Artículo internacional, 2011.

\item Mercadillo, R.E., Díaz, J. L., Pasaye, E. H., Barrios, F. A., "Perception of suffering and compassion experience: 
Brain 
gender disparities", Brain and Cognition 76, 5–14., Créditos en: Artículo internacional, noviembre de 2011.

\item Castillo C.G, Mendoza S., Saavedra J., Giordano M., “Lack of effect of intranigral transplants of a GABAergic cell 
line 
on absence seizures”, Epilepsy \& Behavior., Créditos en: Artículo internacional, noviembre de 2010.

\item PASAYE E.H, GUTIÉRREZ R.A., S. ALCAUTER S., MERCADILLO R.E., AGUILAR-CASTAÑEDA E, DE ITURBE M., ROMERO-ROMO J., 
BARRIOS 
F.A., “Event-Related Functional Magnetic Resonance Images during the Perception of Phantom Limb. A Brushing Task”, The 
Neuroradiology Journal 23: 665-670., Créditos en: Artículo internacional, noviembre de 2010.

\item ROMERO-ROMO J.I, BAUER C.C.C, PASAYE E.H., GUTIÉRREZ R.A., FAVILA R., BARRIOS F.A., “Abnormal Functioning of the 
Thalamocortical System Underlies the Conscious Awareness of the Phantom Limb Phenomenon”, The Neuroradiology Journal 23: 
671-679., Créditos en: Artículo internacional, noviembre de 2010.

\item Mercadillo, RE, Díaz, JL, Pasaye, EH, Barrios, FA, "Gender differences in brain activation during induced compassion 
experiences", Neuropsychologia, manuscript number: NSY-D-10-00001, Créditos en: Artículo internacional, enero de 2010.

\item Morales, T., Ahuilar, L., Ramos, E., Mena, F., Morgan, C., "Fos Expression induced by milk ingestion in the caudal 
brainstem of neonatal rats", Brain Reseach, 1241, 76-83 , Créditos en: Artículo internacional, 2008.

\item Anguiano, B, García-Solís, P, Delgado, G, and, Aceves, CA, "Uptake and Gene Expression with Antitumoral Doses of 
Iodine 
in Thyroid and Mammary Gland: Evidence That Chronic Administration Has No Harmful Effects", THYROID, 17(9): 851-859, 
Créditos en: Artículo internacional, 2007.

\item Herrera-Alarcón, J, Villagómez-Amezcua, E, González-Padilla E, Jiménez-Severiano, H, "Stereological study of 
postnatal 
testicular development in Blackbelly sheep", Theriogenology, 582591, Créditos en: Artículo internacional, 2007.

\item Medina, AC, Charles, JR, Espinoza-González, V, Sánchez-Resendis, O, Prado-Alcalá, RA, Roozendaal, B, and Quirarte, 
GL, 
"Glucocorticoid administration into the dorsal stratium facilitates memory consolidation of inhibitory avoidance training 
but not of the context or footshock components", Learning \& Memory, 673-677, Créditos en: Artículo internacional, mayo de 
2007.

\item Castillo, C.G., Mendoza, S., Freed., W.J., Giordano, M., "Intranigral transplants of immortalized GABAergic cells 
decrease the expression of kainic acid-induced seizures in the rat", Behavioural Brain Research, 171, 109-115, Créditos en: 
Artículo internacional, 2006.

\item Zugasti-Cruz, A., Maillo, M., López-Vera, E., Falcón, A., Heimer de la Cotera, E.P., Olivera, B., M., Aguilar, M.B., 
Amino acid sequence and biological activity of a gama-conotoxin-like peptide from the worm-hunting snail, Peptides 27, 
506-611, Créditos en: Artículo internacional, 2006.

\item Frias, C., Torrero, C., Regalado, M., and Salas., M., Organization of olfactory glomeruli in neonatally 
undernourished 
rats, Nutritional Neuroscience, 1-7, Créditos en: Artículo internacional, 2006.

\item Aguilar, M. B. , Lopez-Vera, E., Imperial, J. S., Falcon, A., Olivera, B. M., De la Cotera, E. P., “Putative 
gamma-conotoxins in vermivorous cone snails: the case of Conus delessertii”, Peptides. 26:23-7, Créditos en: Artículo 
internacional, mayo de 2005.

\item Luna, M., Barraza, N., Berumen, L., Carranza, M., Pedernera, E., Harvey, S., Arámburo, C., “Heterogeneity of growth 
hormone immunoreactivity in lymphoid tissues and changes during ontogeny in domestic fowl”, Gen. Comp. Endocrinol., 
144:28-37, Créditos en: Artículo internacional, mayo de 2005.

\item Aguilar, M. B. , Lopez-Vera, E., Ortiz, E., Becerril, B., Possani, L., D., Olivera, B. M., De la Cotera, E. P., “A 
novel conotoxin from conos delessertii with posttranslationally modified lisien residues”, Biochemistry, 
44:11130-11136, Créditos en: Artículo internacional, mayo de 2005.

\item Cepeda-Nieto, A. C., Pfaff, S. L., Varela-Echavarría, A., “Homeodomain transcription factors in the development of 
subsets of hindbrain reticulospinal neurons”, Mol. Cell Neurosci., 28:30-41, Créditos en: Artículo internacional, mayo de 
2005.

\item García-Solís, P, Alfaro, Y, Anguiano, B, Delgado G, Guzman, R. C. , Nandi, S., Díaz-Muñoz, M., Vazquez-Martinez, O., 
Aceves, C., “Inhibition of N-methyl-N-nitrosourea-induced mammary carcinogenesis by molecular iodine (I2) but not by iodide 
(I-) treatment Evidence that I2 prevents cancer promotion”, Mol. Cell Endocrinol., 236:49-57, Créditos en: Artículo 
internacional, mayo de 2005.

\item Arroyo-Helguera, O., Mejia-Viggiano, C., Varela-Echavarria, A., Cajero-Juárez, M., Aceves, C., “Regulatory role of 
the 
3I untranslated region (3’UTR) of rat 5I deiodinase (D1). Effects on Messenger RNA translation and stability”, Endocrine, 
27:219-227, Créditos en: Artículo internacional, mayo de 2005.

\item Granados-Rojas, L., Aguilar, A., Díaz-Cintra, S., “The mossy fiber system of the hippocampal formation is decreased 
by 
chronic and postnatal but not by prenatal protein malnutrition in rats”, Nutr. Neurosci., 7:301-8, Créditos en: Artículo 
internacional, mayo de 2004.

\item Peréz-León, J.A., Sarabia, G., Miledi, R, Garcia-Alcocer, G., “Distribution of 5hydroxytriptamine2C receptor RNA in 
rat 
retina”, Brain Res Mol Brain Res. 125:140-2, Créditos en: Artículo internacional, mayo de 2004.

\item Anguiano, B., Rojas-Huidobro, R., Delgado, G., Aceves, C., “Has the mammary gland a protective mechanism against 
overexposure to triiodothyronine during the peripartum period? The prolactin pulse down-regulates mammary type I deiodinase 
responsiveness to norepinephrine”, J. Endocrinol., 183:267-77, Créditos en: Artículo internacional, mayo de 2004.

\item Díaz del Guante, M.A., Rivas, M., Prado-Alcalá, R. A., Quirarte, G. L., Amnesia produced by pretraining infusion of 
serotonin into the substantia nigra, SYNAPTIC TRANSMISSION NEUROREPORT, Vol. 15, No. 15, 2527-2529, Créditos en: Artículo 
internacional, 2004.

\item Luna, M., Huerta, L, Berumen, L, Martínez-Coria, H., Harvey, S., Arámburo, C., “Growth hormone in the male 
reproductive 
tract of the chicken: heterogeneity and changes during ontogeny and maturation”, Gen. Comp. Endocrinol. 137:37-49, Créditos 
en: Artículo internacional, mayo de 2004.

\item Díaz-Cintra, S, Yong A, Aguilar A, Bi, X., Lynch, G., Ribak, C.E., “Ultrastructural analysis of hippocampal piramidal 
neurons from apolipoprotein E-deficient mice treated with a cathepsin inhibitor”, J. Neurocytol. 33:37-48, Créditos en: 
Artículo internacional, mayo de 2004.

\item Mena-Segovia, J., Favila, R., Giordano, M., “Long-term effects of striatal lesions on c-Fos immunoreactivity in the 
pedunculopontine nucleus”, Eur. J. Neurosci., 20:2367-76, Créditos en: Artículo internacional, mayo de 2004.

\item López-Vera, E., de la Cotera, E. P., Maillo, M., Riesgo-Escovar, J., Olivera, B. M., Aguilar, M. B., “A novel 
structural class of toxins: the methionine-rich peptides from the venoms of turrid marine snails (Mollusca, Conoidea)”, 
Toxicon., 43:365-74, Créditos en: Artículo internacional, mayo de 2004.

\item Berumen, L. C., Luna, M., Carranza, M., Martinez-Coria, H., Reyes, M., Carabez, A., Arámburo, C., “Chicken growth 
hormone: further characterization and ontogenic changes of an N-glycosylated isoform in the anterior pituitary gland”, Gen. 
Comp. Endocrinol., 139:113-23, Créditos en: Artículo internacional, mayo de 2004.

\item Mena-Segovia, J., Giordano, M., “Striatal dopaminergic stimulation produces c-Fos expression in the PPT and an 
increase 
in wakefulness”, Brain Res., 986:30-8, Créditos en: Artículo internacional, mayo de 2003.

\item Prado-Alcalá, R. A., Solana-Figueroa, R., Galindo, L. E., Medina, AC, Quitarte, G. L., “Blockade of striatal 5-HT2 
receptors produces retrograde amnesia in rats”, Life Sci., 74:481-8, Créditos en: Artículo internacional, mayo de 2003.

\item Vázquez-Martínez, O., Cañedo-Merino, R., Díaz-Muñoz, M., Riesgo-Escovar, “Biochemical characterization, distribution 
and phylogenetic analysis of Drosophila melanogaster ryanodine and IP3 receptors, and thapsigargin-sensitive Ca2+ ATPase”, 
J. Cell Sci., 116:2483-94, Créditos en: Artículo internacional, mayo de 2003.

\item Prado-Alcalá, R. A., Ruiloba, M. I., Rubio, L., Solana-Figueroa, R., Medina, C., Salado-Castillo, R., Quitarte, G. 
L., 
“Regional infusions of serotonin into the striatum and memory consolidation”, Synapse, 47:169-75, Créditos en: Artículo 
internacional, mayo de 2003.

\item Hernádez-Montiel, H. L., Meléndez-Herrera, E., Cepeda-Nieto, A. C., Mejía-Viggiano, C., LarrivaSahd, J., Guthrie, S., 
Varela-Echavarría, A.”Diffusible signals and fasciculated growth in reticulospinal axon pathfinding in the hindbrain”, Dev. 
Biol., 255:99-112, Créditos en: Artículo internacional, mayo de 2003.

\item Mena-Segovia, J., Cintra, L., Prospéro-Garcia, O., Giordano, M. “Changes in sleep-waking cycle after striatal 
excitotoxic lesions”, Behav. Brain Res., 136:475-81, Créditos en: Artículo internacional, mayo de 2002.

\item Marina, N., Morales, T., Díaz, N., Mena, F., “Suckling-induced activation of neural c-fos expression at lower 
thoracic 
rat spinal cord segments”, Brain Res., 954:100-14, Créditos en: Artículo internacional, mayo de 2002.

\item Larriva-Sahd, J., Condés Lara, M., Martínez-Cabrera, G., Varela-Echavarría, A., “Histological and ultrastructural 
characterization of interfascicular neurons in the rat anterior commissure”, Brain Res., 931:81-91, Créditos en: Artículo 
internacional, mayo de 2002.

\item Martínez-Coria, H., López-Rosales, L. J., Carranza, M., Berumen, L., Luna, M., Arámburo, C., “Differential secretion 
of 
chicken growth hormone variants after growth hormone-releasing hormone stimulation in Vitro”, Endocrine, 17:91-102, 
Créditos en: Artículo internacional, mayo de 2002.

\item Solana-Figueroa, R., Salado-Castillo, R., Galindo, L. E., Quitarte, G. L., Prado-Alcalá, R. A., “Effects of 
pretraining 
intrastriatal administration of p-chloroamphetamine on inhibitory avoidance”, Neurobiol Learn Mem., 78:178-85, Créditos en: 
Artículo internacional, mayo de 2002.

\item Díaz, N., Huerta, I., Marina, N., Navarro, N., Mena, F., “Regional mechanisms within anterior pituitary of lactating 
rats may regulate prolactin secretion”, Endocrine, 18:41-6, Créditos en: Artículo internacional, mayo de 2002.

\item Martinez, I., Quitarte, G. L., Díaz-Cintra, S., Quiroz, C., Prado-Alcala, R. A., “Effects of lesions of hippocampal 
fields CA1 and CA3 on acquisition of inhibitory avoidance”, Neuropsychobiology, 46:97103, Créditos en: Artículo 
internacional, mayo de 2002.

\item Giordano, M., Mejía-Viggiano, M. C., “Gender differences in spontaneous and MK-801-induced activity alter striatal 
lesions”, Brain Res. Bull., 56:553-61, Créditos en: Artículo internacional, mayo de 2001.

\item Fernández-Bouzas, A., Harmony, T., Fernández, T., Silva-Pereyra, J., Valdés, P., Bosch, J., Aubert, E., Casian, G., 
Otero Ojeda, G., Ricardo, J., Hernandez-Ballesteros, A., Santiago, E., “Sources of abnormal EEG activity in brain 
infarctions”, Clin. Electroencephalogr., 31:165-9, Créditos en: Artículo internacional, mayo de 2000.

\item Arámburo, C., Luna, M., Carranza, M., Reyes, M., Martínez-Coria, H., Scanes, C. G., “Growth hormone size variants: 
changes in the pituitary during development of the chicken”, Proc. Soc. Exp. Biol. Med., 223:67-74, Créditos en: Artículo 
internacional, mayo de 2000.

\item Aguilar, M.B., Lezama-Monfil, L., Maillo, M., Pedraza-Lara, H., López-Vera E., Heimer de la Cotera, E.P., "A 
biologically active hydrophobic T-1-conotoxin from the venom of Conus spurius", Peptides, 27, 500-505, Créditos en: 
Artículo internacional, 2000.

\item García-Colunga, J., Valdiosera, R., García, U., “P-type Ca2+ current in crayfish peptidergic neurones”, J. Exp, 
Biol., 
202:429-440, Créditos en: Artículo internacional, mayo de 1999.

\item Dueñas, Z., Torner, L., Corbacho, A. M., Ochoa, A., Gutiérrez-Ospina, G., López-Barrera, F., Barrios, F. A., Berger, 
P., Martínez de la Escalera, G., Clapp, C., “Inhibition of rat corneal angiogenesis by 16-kDa prolactin and by Endogenous 
prolactin-like molecules”, Invest. Ophthalmol. Vis. Sci., 40:2498-505, Créditos en: Artículo internacional, mayo de 1999.

\item Gutiérrez-Ospina, G., Jiménez-Trejo, F. J., Favila, R., Moreno-Mendoza, N. A., Granados Rojas, Barrios, F. A., 
Diaz-Cintra, S., Merchant-Larios, H., “Acetylcholinesterase-positive innervation is present at undifferentiated stages of 
the sea turtle Lepidochelis olivacea embryo gonads: implications for temperature-dependent sex determination”, J. Comp. 
Neurol., 410:90-8, Créditos en: Artículo internacional, mayo de 1999.

\item Gutiérrez-Ospina, G., Díaz-Cintra, S., Aguirre-Portilla, A., Aguilar-Vázquez, A., López, S. R., Barrios, F.A., 
“Comparable activity levels in developmentally deprived and non-deprived layer IV cortical columns of the adult rat primary 
somatosensory cortex”, Neurosci. Lett., 247:5-8, Créditos en: Artículo internacional, mayo de 1998.

\item Giordano, M., Salado-Castillo, R., Sánchez-Alvarez, M., Prado-Alcalá, R. A., “Striatal transplants prevent 
AF64A-induced retention deficits”, Life Sci., 63:1953-61, Créditos en: Artículo internacional, mayo de 1998.

\end{enumerate}

