\textbf{Artículos Publicados}

\hfill

\begin{enumerate}

\item Hevia-Orozco, J.C., Reyes-Aguilar, A., Hernández-Pérez, R., González-Santos, L., Pasay, E H., Barrios, F.A., Personality 
Traits Induce Different Brain Patterns When Processing Social and Valence Information, Frontiers in Physiology, 1-9, enero de 2022.

\item Romero-Meléndez, C. , Castillo-Fernández, D. and González-Santos, L., “On the Boundedness of the Numerical Solutions’ 
Mean Value in a Stochastic Lotka–Volterra Model and the Turnpike Property“, Hindaw Complexity, 1-14, noviembre de 2021.

\item Romero-Meléndez, C., González-Santos, L., Castillo-Fernández, “A NUMERICAL APPROACH FOR THE STOCHASTIC CONTROL OF A 
TWO-LEVEL QUANTUM SYSTEM”, CYBERNETICS AND PHYSICS, 9(2), 107-116, agosto de 2020.

\item Velásquez-Upegui, E.P., Tovar-González, J., González, L., “Hacia una caracterización prosódica de los actos del habla 
directivos: producción y percepción de mandatos”, Lengua y Habla, Revista del Centro de Investigación y Atención 
Lingüística C.I.A.L, 24, 1-5, agosto de 2020.

\item Muley, V.Y., López-Victorio, C.J., Ayala-Sumuano, J.T., González-Gallardo, A., González-Santos, L., Lozano-Flores, C., 
Wray, G., Hernández-Rosales, M., Varela-Echavarría, A., “Conserved and divergent expression dynamics during early 
patterning of the T telencephalon in mouse and chick embryos”, Progress In Neurobiology, 186, 1-15, enero de 2020.

\item Martínez-Soto, J., De la Fuente Suárez, L.A., González-Santos, L., Barrios, F.A., “Observation of environments with 
different restorative potential results in differences in eye patron movements and pupillary size”, IBRO Reports, 7, 52-58, noviembre de 2019.

\item Nanni, M., Martínez-Soto, J., González-Santos, L., Barrios, F.A., "Neural correlates of the natural observationof an 
emotionally loaded video", Plos One, 1-19, noviembre de 2018.

\item Martinez J, Gonzalez-Santos L, Barrios F.A., AFFECTIVE AND RESTORATIVE VALENCES FOR THREE ENVIRONMENTAL CATEGORIES, 
Perceptual And Motor Skills, 1-10, octubre de 2014.

\item Beatriz Moreno M., Concha L., González-Santos L., Ortiz J.J., Barrios F.A., , Correlation between Corpus Callosum 
Sub-Segmental Area and Cognitive Processes in School-Age Children, Plos One, 1-10, agosto de 2014.

\item Bauer C.C., Moreno B., Gonzalez-Santos L., Concha L., Barquera S., Barrios F.A., Child overweight and obesity are 
associated with reduced executive cognitive performance and brain alterations: a magnetic resonance imaging study in 
Mexican children, Pediatric Obesity, julio de 2014.

\item Martínez-Soto J., González-Santos L., Pasaye E. and Barrios F.A., Exploration of neural Correlates of restorative 
environment exposure through functional magnetic resonance, Intelligent Buildings International, Taylor Francis Online, 5(S1), 10-28, septiembre de 2013.

\item Gonzalez-Santos L, Mercadillo RE, Graff A, Barrios FA, "Versión computarizada para la aplicación del Listado de 
Síntomas 90 (SCL 90) y del Inventario de Temperamento y Carácter (ITC)", Salud Mental, 30(4), 31-40, julio de 2007.

\item Barríos F.A., González L., Fávila R., Alonso M.E., Salgado P., Díaz R., Fenández, J., OLFACTION AND NEURODEGENERATION 
IN HD, Neuroreport, 18(1), 73-76, enero de 2007.

\item Huerta-Ocampo I., Mena F., Barríos F.A., Martínez G., González L., Larriva-Sahd J.L., Perinatal Exposure to Androgen 
Suppresses Sexual Dimorphism in Nerve Trunk Diameter, Axon Number, and Fiber Size Spectrum: a Quantitative Ultrastructural 
Study of the Adult Rat Mammary Nerve., Brain Research, 1060(1-2), 179-183, octubre de 2005.

\item George-Téllez R, Segura-Valdez ML, González-Santos L, Jiménez-García LF, "Cellular organization of pre-mRNA splicing 
factors in several tissues. Changes in the uterus by hormone action", Biology of the cell, 94(2), 99-108, mayo de 2002.

\item González-Santos, L., Rojas-Jasso, R., Salgado, P., Ponte-Romero, R., Sánchez-Cortázar, J., Barrios, F.A., "Segmentación 
semiautomática de imágenes por resonancia magnética cerebral por crecimiento de regiones con estimación robusta: una 
validación radiológica", Revista Mexicana De Radiologia, 53(2), 51-54, abril de 1999.

\end{enumerate}
