4
Graphical Analysis

4.1
Graphical Analysis

4.2
Orbit Analysis

4.3
The Phase Portrait

Exercises
1. Use graphical analysis to describe the fate of all orbits for each of the
following functions. Use diﬀerent colors for orbits that behave diﬀerently.

a. F (x) = 2x
b. F (x) = 1/3x
c. F (x) = -2x + 1
d. $F(x) = x^2$
e. $F(x) = -x^3$
f. $F(x) = x - x^2$
g. $S(x) = \sin x$

2. Use graphical analysis to ﬁnd $\{x0 | F^n(x_0 ) →  ±∞}$ for each of the following
functions.

a. F (x) = 2x(1 − x)
b. $F(x) = x^2 + 1$
c. T (x) =
2x
2 − 2x
x ≤ 1/2
x > 1/2

3. Sketch the phase portraits for each of the functions in exercise 1.
4. Perform a complete orbit analysis for each of the following functions.

a. $F(x) = \frac{1}{2} x - 2$
b. A(x) = |x|
c. $F(x) = -x^2$
d. $F(x) = -x^5$
e. F (x) = 1/x
f. $E(x) = e^x$

5. Let F (x) = |x - 2|. Use graphical analysis to display a variety of orbits of
F . Use red to display cycles of period 2, blue for eventually ﬁxed orbits, and
green for orbits that are eventually periodic.

6. Consider $F(x) = x^2 - 1.1$. First ﬁnd the ﬁxed points of F . Then use the
fact that these points are also solutions of $F^2(x) = x$ to ﬁnd the cycle of prime
period 2 for F .

7. All of the following exercises deal with dynamics of linear functions of the
form F (x) = ax + b where a and b are constants.

a. Find the ﬁxed points of F (x) = ax + b.
b. For which values of a and b does F have no ﬁxed points?
c. For which values of a and b does F have inﬁnitely many ﬁxed points?
d. For which values of a and b does F have exactly one ﬁxed point?
e. Suppose F has just one ﬁxed point and 0 < |a| < 1. Using graphical
analysis, what can you say about the behavior of all other orbits of
F ? We will call these ﬁxed points attracting ﬁxed points later. Why
do we use this terminology?
f. What is the behavior of all orbits when a = 0?
g. Suppose F has just one ﬁxed point and |a| > 1. Using graphical
analysis, what can you say about the behavior of all other orbits of
F in this case? We call such ﬁxed points repelling. Can you explain
why?
h. Perform a complete orbit analysis for F (x) = x + b in cases $b > 0$,
b = 0, and $b < 0$.
i Perform a complete orbit analysis for F (x) = -x + b.


